Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-19 Submission.Rmd
figured out zero sd's. We were reading in the "truncated labels" .csv file improperly (labels were misaligned with variables)

labels <- read.csv("truncatedlabels.csv")

@@

resource <- resource[,-145]   ## attention check
#resource <- resource[ which(resource$sd > 0), ]

@@

challenge <- challenge[,-308]

@@

hindrance <- hindrance[,-248]   ## attention check
#hindrance <- hindrance[ which(hindrance$sd > 0), ]

@@

labels <- read.csv("truncatedlabels.csv")

resource <- resource[,-145]   ## attention check
#resource <- resource[ which(resource$sd > 0), ] 
########################################################
########################################################
##Need to triple check all of this. 
########################################################
########################################################
##checking the ns
#library(psych)
#resource_ns <- describe(data[c(118:144, 146:202)])
#resource_ns
#table(data$item161) # check one item to confirm ns - it is functioning correctly.

#resource <- cbind(resource, resource_ns$n)
#resource
sortresource <- resource[order(resource$sd),]

@@

labels <- read.csv("truncatedlabels.csv")

challenge <- challenge[,-308]   ## attention check
#challenge <- challenge[ which(challenge$sd > 0), ]

@@

labels <- read.csv("truncatedlabels.csv")

hindrance <- hindrance[,-248]   ## attention check
#hindrance <- hindrance[ which(hindrance$sd > 0), ]

@@

labels <- read.csv("truncatedlabels.csv")

resource <- resource[,-145]   ## attention check
resource <- resource[ which(resource$sd > 0), ]

@@

labels <- read.csv("truncatedlabels.csv")

challenge <- challenge[,-308]   ## attention check
challenge <- challenge[ which(challenge$sd > 0), ]

@@

labels <- read.csv("truncatedlabels.csv")

hindrance <- hindrance[,-248]   ## attention check
hindrance <- hindrance[ which(hindrance$sd > 0), ]

>>>>

labels <- read.csv("truncatedlabels.csv", header=FALSE)  ## Changed on 12/19 to fix zero sd issues

@@

resource <- resource[-28,]   ## attention check

@@

challenge <- challenge[-21,]

@@

hindrance <- hindrance[-46,]   ## attention check = 248

@@

sortresource <- resource[order(resource$sd),]

@@

@@

@@

resource <- resource[ which(resource$sd > 0), ]

@@

@@

### 2022-12-19 Submission.tex
figured out zero sd's. We were reading in the "truncated labels" .csv file improperly (labels were misaligned with variables)

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 0 to 1.18. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0 to 0.88 and the range of lowest 10 challenge standard deviations is 0 to 0.87.

>>>>

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.19. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0.70 to 0.88 and the range of lowest 10 challenge standard deviations is 0.79 to 0.87.
